---
title: "GoogleApps EDA"
author: "Dr Ada Ajunwa"
date: "January 11, 2019"
output: html_document
---

Load data and libraries

```{r}
googleplaystore_original <- read.csv("~/Data Science/googleplaystore_original_Clean.csv")
head(googleplaystore_original)
library("dplyr")
library("stringr")
library("ggplot2")
```
The density graph below shows that Rating has an outlier with value 19
Remove outlier
Density graph now shows that Rating is left skewed
```{r}
googleplaystore_original$Installs <- as.character(googleplaystore_original$Installs)
googleplaystore_original$Installs<- ordered(googleplaystore_original$Installs, levels=c("NA","0","1","5","10","50","100","500","1000","5000","10000","50000","100000","500000","1000000","5000000","10000000","50000000","100000000","500000000", "1000000000"))
ggplot(googleplaystore_original, aes(Rating)) +geom_density()
googleplaystore_original<-filter(googleplaystore_original,Rating != 19)
ggplot(googleplaystore_original, aes(Rating)) +geom_density()
```

Distinct number of app categories is 33
Top 50% of apps by category (top 3 categories are Family, Game and Tools)
```{r}
distinct(googleplaystore_original,Category)
top_50_category<-arrange(top_n(count(googleplaystore_original, Category), n=17),desc(n))
ggplot(inner_join(googleplaystore_original, top_50_category, by = "Category"), aes(AdjustedInstall, fill=Category)) +geom_bar()+facet_grid(Category ~ .)
```
Among apps with extremely small downloads (1-500), Family apps have the largest presence, followed by Tool apps, then Medical apps 
Among apps with very small downloads (1000-10000), Family apps have the largest presence, followed by Tool apps, then Medical apps 
Among apps with small downloads (50000-500000), Family apps have the largest presence, followed by Gaming apps, then Tool apps 
Among apps with medium downloads (1000000-10000000), Family apps have the largest presence, followed by Gaming apps, then Tool apps 
Among apps with large downloads (50000000-500000000), Gaming apps have the largest presence, followed by Family apps, then Communication apps 
Among apps with very large downloads (50000000-500000000), Communication apps have the largest presence, followed by Social apps, then Gaming apps 
```{r}
ggplot(filter(googleplaystore_original,AdjustedInstall =="Extremely Small"), aes(Category, fill= Category)) +geom_bar()
ggplot(filter(googleplaystore_original,AdjustedInstall =="Very Small"), aes(Category, fill= Category)) +geom_bar()
ggplot(filter(googleplaystore_original,AdjustedInstall =="Small"), aes(Category, fill= Category)) +geom_bar()
ggplot(filter(googleplaystore_original,AdjustedInstall =="Medium"), aes(Category, fill= Category)) +geom_bar()
ggplot(filter(googleplaystore_original,AdjustedInstall =="Large"), aes(Category, fill= Category)) +geom_bar()
```

The scatter plot below shows that Rating has a weak positive effect on Installs (number of downloads). Therefore, higher ratings, bring about more downloads
```{r}
ggplot(googleplaystore_original, aes(x=Rating, y= Installs)) +geom_point()
```

To see how number of Installs are affected by sum of Ratings
The scatter plot below shows that the sum of Ratings has a strong positive effect on Installs
```{r}
installs_by_sum_rating <- aggregate(as.numeric(googleplaystore_original[, 3]), list(googleplaystore_original$Installs), sum, na.rm=TRUE)
colnames(installs_by_sum_rating)[1] <- "Installs"
colnames(installs_by_sum_rating)[2] <- "SumRating"
ggplot(installs_by_sum_rating, aes(x=SumRating, y= Installs)) +geom_point()
```

The scatter plot below shows that SizeKB (App size) seems to have a very weak positive effect on Installs (number of downloads)
```{r}
ggplot(googleplaystore_original, aes(x=SizeKB, y= Installs)) +geom_point()
```

The scatter plot below shows that Reviews (number of reviews) has no effect on Installs (number of downloads)
```{r}
ggplot(googleplaystore_original, aes(x=SizeKB, y= Installs)) +geom_point()
```

The bar chart shows that paid Apps had less downloads than free Apps and less Apps where paid for
```{r}
ggplot(googleplaystore_original, aes(Installs, fill=Type)) +geom_bar()+facet_grid(Type ~ .)
ggplot(googleplaystore_original, aes(AdjustedInstall, fill=Type)) +geom_bar()+facet_grid(Type ~ .)
```

The scatter plot below shows that SizeKB (app size) has no effeCT on Installs(number of downloads)
```{r}
ggplot(googleplaystore_original, aes(x=SizeKB, y= Installs)) +geom_point()
```

The bar chart below shows that apps that require a minimum install versions in the 4s are the most downloaded accross all install levels. This is followed by apps that require version 2s
```{r}
ggplot(filter(googleplaystore_original, MinimumVer!="NA"), aes( x= AdjustedInstall, fill =MinimumVer)) +geom_bar(position = "dodge")
```

The bar chart below shows that apps that require a minimum install version in the 2s were downloaded most between 2011 and 2015.Downloads of apps requiring version 4s took over in 2016, and grew exponentialy all the way to 2018
```{r}
ggplot(filter(googleplaystore_original, MinimumVer!="NA"), aes( x= Year, fill =MinimumVer)) +geom_bar(position = "dodge")
```